Transforming Trash as an Artistic Act

### 2015-12-29 chapter2_reduced.tex
thesis format
Former-commit-id: 45314951bf19c52d30f0c36d2e22e1c79e2717e1

Firstly, focused on the disposable items that are designed to be ended up in waste bin after a single use. Their usage and place are examined in the society and how other artists used and transformed them is analyzed. Further, disposable items are one of the key material used in the thesis project. Therefore, they need to be discussed in detail.

Secondly, looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.

@@

% Life Magazine, 1955, "Throwaway Living", p43
\summary{Throwaway Society} 
Life magazine published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955 \todo{ref}. It is described as behavioral consumption pattern of society based on throwing away objects after use. The article addresses the question of 
% https://nerc.org/news-and-updates/blog/nerc-blog/2014/01/14/throw-away-society
\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use? \todo{cite}} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.

According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth. \todo{ref. rathje1992rubbish p41}

On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \cite{gregson2007identity}. According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys. However, their research did not include disposable packaging and bottles. Therefore, the act of throwing away can be narrowed down the specific goods.

In this thesis dealt specifically with industrially produced consumer discards and their subsequent transformation. This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century. In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production \todo{ref. Mamiya 1992, 2}.

@@

%
%
\summary{Disposable Items}
Disposable items are made to be thrown away after used once or only a few times. They are not permanent or durable and not designed to reuse again. Packages of beverages, paper cups and tissues are some of them. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. However, their usage duration is very short, they continue to exist in nature.

@@

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\summary{Life of an Object} 
One could claim that the end of the life of an object corresponds to the moment when it is refused. This action might take place in different forms and for various reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste. At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values. \todo{ref. emgin2012trashion p.63}

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new. The capacity for serial replacement is also the capacity to throw away without concern.”} \todo{ref. hawkins2001plastic p.9, emgin2012trashion p.64}

@@

\summary{Capitalism, market, encouragement} 
\paraphrase{The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap. They were designed to decrease in value over time - to be used one, or twice and then to be thrown away. This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.} \todo{ref. cerny1996recycled}

\summary{Initial function} 
\paraphrase{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash.} \todo{ref. cerny1996recycled}

\summary{Being wasteful}
As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \todo{ref, hawkins2005ethics p.viii} because the cost of repairing objects sometimes is higher than the original one or very close to it. On the other side, it is refused to use because of they are old fashioned even if they are perfectly fine.

%
%
\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. Disposable items with the help of industrialization can be produced easily. Mass production. Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs. wipes, glass vs. paper cup). Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontology}.}

@@

\paraphrase{The germ theory proscribes companionship. The Latin root for this word, cum pani, literally means to share bread. However, insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self. Safety in a world of bacteria implies isolation. Packaging successfully isolates both food and consumer within a structure of sterile control. In essence, it encloses the commons. Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.} \todo{ref. ontology of trash}

@@

\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
\end{quote}

\summary{Dark side} 
Usage of disposable items in the society is very widespread. For same cases it is inevitable. Beyond the advantages of disposable items, there are side effects of consuming them excessively. They result in mountains of garbage.

@@

%
%
\summary{Art}
There are some artists whose works are related to the phenomena expressed above. (Some of the works of the artist can be examined in this phenomena.) Not every person throw away disposable objects, some of them save them and use for their purposes. They establish some methods to reflect the throwaway culture and its consumption and trash generated patterns.

@@

\paraphrase{Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. It is one of the pieces of Portraits of Global Mass Culture by Chris Jordan is a series of work. In this series, he revisits the statistics of modern societies.  In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.}

\summary{Analysis}
In fact, the work of Chris Jordan is a reproduction of A Sunday Afternoon on the Island of La Grande Jatte which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism. The work accepted as a well-known example of pointilizm that is a technique of painting in which little, individual dots of color are applied in patterns to form an image. This method shows similarities with mosaics of ancient times and pixels of modern times. To make an work from bottle cups with different colors can be related to painting millions of small dots on a canvas. The shape of plastics cups similar to the dots painted onto the canvas so that there could not be a better example of reproduction.

@@

\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations. The artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Endeavour of re-purposing recycled and found materials.} \todo{cite website}

\summary{Analysis}
This work is for fathers day. Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day). Trashes transformed to diaries. Trash is everywhere, already at hand. Small pieces of paper or packages are used as a canvas.

@@

\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of our throwaway caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. Moreover, on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup is representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. However, as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. Paintings on paper coffee cups displayed in open window spaces. She publicly draws their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects, she draws with other people. Moreover, so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transforms its cup.} \todo{cite her website}

\summary{Analysis}
She is inside of glass window not white, isolated cube. Glass window provide her to be close to public space. As she drinks her coffee publicly, also paints them publicly. \todo{related with Liz Parson's argument: practice of trash to durable.} There is no difference between them, and also they should not be separated (Why? Trash, production of it, coffee cups are all experienced widespread.). By showing her practice publicly, she encourages other people in order to reconsider trash as a resource to make something. Further she is not only transforming her trash, it is everybody's trash because of everyone uses it.

@@

\summary{TRASH and POTRAIT OF PEOPLE} 
Trash is a reminder of consumption and production activities. In other words, trash is bound to them, and every different of them leaves a diverse range of trash that exposes its type of action. Trash tells about societies choices. What is being left is one of the key things to realize what kind of people, society, action produce it. At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.) \todo{ref.}. As scholars mentioned that throughout the discards of someone else many things can be understood. They are end product of people activities, and it can be traced through the discard and garbage. It is a great example of the approach to the trash is relative and changes from people to people.

@@

\paraphrase{Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had. Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.}

\paraphrase{When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends. Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao opposed their efforts to dispose of things that she saw as potentially useful. Song eventually came to understand that, as he puts it:}

\begin{quote}
My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death. I recognised that in this era of transition, a person could live through several different lives in just one lifetime. In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
\end{quote}

Everything that are exhibited here is different than presented on supermarkets. They are not new and not for sale. They represents a way of life. It is common that the exhibition (museum) of famous people's possessions but this work is separated from them as showing ordinary people's objects

@@

%
%
\summary{Garbology}
Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.

\paraphrase{Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away.}" \cite{lukas2012garbage}}

% Garbology, from Encyclopedia, Abhijit Roy
\paraphrase{The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.}\todo{ref.}

\paraphrase{The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice. At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene. (from Trash Culture)}

\todo{transition required.} With the help of mentioned understanding of trash, what can we see the work of arts?

@@

It is a realization what she did during her depression time. It perfectly represents her condition during days. It can be understood that trash is part of our life. Things that are exhibited in this work are part of her action. She created them and later through them in the mind of people the condition and life of Tracey Emin are recreated.

@@

Beds meaning also are not same for everyone. It is not just for sleep. Especially for the ones that have small rooms and spaces bed becomes a life space. I have also experienced such a thing at boarding school and university dormitory for total my eight years. Having tight space sometimes bed becomes a place for studying and reading. Sometimes it was used to dry the clothes. It is more than sleeping and provide place for other activities.

@@

\paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}

@@

Beyond the ecological problem, there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.

@@

Fountain is a 1917 work produced by Marcel Duchamp, who is notable member of provocative Dada movement. The piece was an industrial porcelain urinal, which was signed "R.Mutt". Submitted for the exhibition of the Society of Independent Artists, in 1917, Fountain was rejected by the committee, even though the rules stated that all works would be accepted from artists who paid the fee. It is considered one of the major artworks of the 20th century because of challenging the existing understanding of art. Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist. It forces to the limits of the language of art and perception the art. To understand his works requires shift inside of the peoples mind. For him, the idea is important rather than the object. He also criticized the position of artist by signing urinal as "R.Mutt" who is actually not exist. In the editorial The Blind Man summarized this work as follows: "Whether Mr. Mutt with his own hands made the fountain or not has no importance. He CHOSE it. He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view – created a new thought for that object.\todo{ref}" To debate all the aspects of this work is not possible with the scope of this thesis. However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist. Urine titled as "fountain" is still functional and have a place in the market. In another word, it is not rubbish.

\todo{bir conslusion lazım buraya.}

>>>>

Firstly, I focused on the disposable items that are designed to be ended up in waste bin after a single use. Their usage and place are examined in the society and how other artists used and transformed them is analyzed. Further, disposable items are one of the key material used in the thesis project. Therefore, they need to be discussed in detail.

Secondly, I looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.

@@

% TODO ref Life Magazine, 1955, "Throwaway Living", p43
%\summary{Throwaway Society} 
%\cite[43]{life1955throwaway} 
Life magazize published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955. It is described as behavioral consumption pattern of society based on throwing away objects after use. The article addresses the question of 
% https://nerc.org/news-and-updates/blog/nerc-blog/2014/01/14/throw-away-society
\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use?} \citep{tully2014throw} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.

According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth \citep[41]{rathje1992rubbish} On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \citep{gregson2007identity}. According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys. However, their research did not include disposable packaging and bottles. Therefore, the act of throwing away can be narrowed down to the specific goods.

In this thesis dealt specifically with industrially produced consumer discards and their subsequent transformation. This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century. In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production 
%\todo{ref. Mamiya 1992, 2}.

@@

%
%
%\summary{Disposable Items}
Disposable items are made to be thrown away after used once or only a few times. They are not permanent or durable and not designed to reuse again. Packages of beverages, paper cups and tissues are some of them. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. However, their usage duration is very short, they continue to exist in nature.

@@

% FROM Trashion: The Return of the Disposed by Bahar Emgin
%\summary{Life of an Object} 
One could claim that the end of the life of an object corresponds to the moment when it is refused. This action might take place in different forms and for various reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste. At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values \citep[63]{emgin2012trashion}.

% FROM Trashion: The Return of the Disposed by Bahar Emgin
%\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
\cite[9]{hawkins2001plastic} argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new. The capacity for serial replacement is also the capacity to throw away without concern.”
%\todo{ref. hawkins2001plastic p.9, emgin2012trashion p.64}

@@

%\summary{Capitalism, market, encouragement} 
The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap \citep{cerny1996recycled}. They were designed to decrease in value over time - to be used one, or twice and then to be thrown away. This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.

%\summary{Initial function} 
\quotes{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash} \citep{cerny1996recycled}.

%\summary{Being wasteful}
As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \citep[viii]{hawkins2005ethics} because the cost of repairing objects sometimes is higher than the original one or very close to it. On the other side, it is refused to use because of they are old fashioned even if they are perfectly fine.

%
%
%\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. Disposable items with the help of industrialization can be produced easily. Mass production. Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs. wipes, glass vs. paper cup). Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \quotes{The commodities of food and drink must be safe, sterile and private} \citep{kennedy2007ontology}.

@@

The germ theory proscribes companionship. The Latin root for this word, cum pani, literally means to share bread. However, insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self. Safety in a world of bacteria implies isolation. Packaging successfully isolates both food and consumer within a structure of sterile control. In essence, it encloses the commons. Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.
%\todo{ref. ontology of trash}

@@

\begin{singlespace}
\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips. \citep{strasser1999waste}
\end{quote}
\end{singlespace}

%\summary{Dark side} 
Usage of disposable items in the society is very widespread. For same cases it is inevitable. Beyond the advantages of disposable items, there are side effects of consuming them excessively. They result in mountains of garbage.

@@

%
%
%\summary{Art}
There are some artists whose works are related to the phenomena expressed above. (Some of the works of the artist can be examined in this phenomena.) Not every person throw away disposable objects, some of them save them and use for their purposes. They establish some methods to reflect the throwaway culture and its consumption and trash generated patterns.

@@

Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. It is one of the pieces of Portraits of Global Mass Culture by Chris Jordan is a series of work. In this series, he revisits the statistics of modern societies.  In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.

%\summary{Analysis}
In fact, the work of Chris Jordan is a reproduction of A Sunday Afternoon on the Island of La Grande Jatte which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism. The work accepted as a well-known example of pointilizm that is a technique of painting in which little, individual dots of color are applied in patterns to form an image. This method shows similarities with mosaics of ancient times and pixels of modern times. To make an work from bottle cups with different colors can be related to painting millions of small dots on a canvas. The shape of plastics cups similar to the dots painted onto the canvas so that there could not be a better example of reproduction.

@@

Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations. The artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Endeavour of re-purposing recycled and found materials. 
%\todo{cite website}

%\summary{Analysis}
This work is for fathers day. Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day). Trashes transformed to diaries. Trash is everywhere, already at hand. Small pieces of paper or packages are used as a canvas.

@@

She saves all of her coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of our throwaway caffeine culture. She uses cups as a surface on which to draw and paint. Moreover, on the bottom of each one, She record the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup is representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. However, as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. Paintings on paper coffee cups displayed in open window spaces. She publicly draws their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects, she draws with other people. Moreover, so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transforms its cup.
%\todo{cite her website}

%\summary{Analysis}
She is inside of glass window not white, isolated cube. Glass window provide her to be close to public space. As she drinks her coffee publicly, also paints them publicly. 
%\todo{related with Liz Parson's argument: practice of trash to durable.} 
There is no difference between them, and also they should not be separated. By showing her practice publicly, she encourages other people in order to reconsider trash as a resource to make something. Further she is not only transforming her trash, it is everybody's trash because of everyone uses it.

@@

%\summary{TRASH and POTRAIT OF PEOPLE} 
Trash is a reminder of consumption and production activities. In other words, trash is bound to them, and every different of them leaves a diverse range of trash that exposes its type of action. Trash tells about societies' choices. What is being left is one of the key things to realize what kind of people, society, action produce it. At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.) 
%\todo{ref.}
. As scholars mentioned that throughout the discards of someone else many things can be understood. They are end product of people activities, and it can be traced through the discard and garbage. It is a great example of the approach to the trash is relative and changes from people to people.

@@

Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had. Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.

When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends. Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao opposed their efforts to dispose of things that she saw as potentially useful. Song eventually came to understand that, as he puts it:

\begin{singlespace}
\begin{quote}
My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death. I recognised that in this era of transition, a person could live through several different lives in just one lifetime. In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
\end{quote}
\end{singlespace}

Everything that are exhibited here is different than presented on supermarkets. They are not new and not for sale. They represent a way of life. It is common that the exhibition (museum) of famous people's possessions but this work is separated from them as showing ordinary people's objects

@@

%
%
%\summary{Garbology}
Garbology is a study of waste as a social science. Applying methodologies of archeology to the human debris.

Weberman infamously used techniques of what he deemed garbology to uncover what he saw as the essential nature of people. He once said, perhaps indirectly referencing Jean Brillat-Savarin’s quote about food, \quotes{You are what you throw away} \citep{lukas2012garbage}.

% Garbology, from Encyclopedia, Abhijit Roy
The field of garbology involves the study of refuse and waste. It enables researchers to document information on the nature and changing patterns of modern refuse, hence assisting in the study of contemporary human society or culture \citep{roy2012garbology}. According to the Oxford English Dictionary, the term was first used by waste collectors in the 1960s. Weberman popularized the term in describing his study of Bob Dylan’s garbage in 1970. It was pioneered as an academic discipline by William Rathje at the University of Arizona in 1973.
%roy2012garbology

The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice. At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene \citep{pye2010trashculture}.

%\todo{transition required.} 
With the help of mentioned understanding of trash, what can we see the work of arts?

@@

It is a realization what she did during her depression time. It perfectly represents her condition during those days. It can be understood that trash is part of our life. Things that are exhibited in this work are part of her action. She created them and later through them in the mind of people the condition and life of Tracey Emin are recreated.

@@

Beds are not just for sleep. Especially for the ones that have small rooms and spaces bed becomes a life space. I have also experienced such a thing at boarding school and university dormitory for total my eight years. Having tight space sometimes bed becomes a place for studying and reading. Sometimes it was used to dry the clothes. It is more than sleeping and provide place for other activities.

% tracey emin joseph beuys arasında bir ilişki var. sanatsal eylem ve kalıntı olarak bakıldığında.

@@

\begin{singlespace}
\begin{quote}
In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects \citep[5]{hawkins2005ethics}.
\end{quote}
\end{singlespace}

@@

%Beyond the ecological problem, there are different sides of it. Different readings can be added to the topic. Adding spirituality and new aesthetics dimension to the topic.

@@

Fountain is a 1917 work produced by Marcel Duchamp, who is notable member of provocative Dada movement. The piece was an industrial porcelain urinal, which was signed "R.Mutt". Submitted for the exhibition of the Society of Independent Artists, in 1917, Fountain was rejected by the committee, even though the rules stated that all works would be accepted from artists who paid the fee. It is considered one of the major artworks of the 20th century because of challenging the existing understanding of art. Duchamp used already existing fabricated ordinary urinal to express his ideas by challenging existing way of art making which requires efforts of the artist. It forces to the limits of the language of art and perception the art. To understand his works requires shift inside of the peoples mind. For him, the idea is important rather than the object. He also criticized the position of artist by signing urinal as "R.Mutt" who is actually not exist. In the editorial The Blind Man summarized this work as follows: \quotes{Whether Mr. Mutt with his own hands made the fountain or not has no importance. He CHOSE it. He took an ordinary article of life, placed it so that its useful significance disappeared under the new title and point of view – created a new thought for that object} \citep{duchamp1917mutt}. To debate all the aspects of this work is not possible with the scope of this thesis. However when it is analyzed through the frame of rubbish theory, urinal a transient object turned to durable objects that are exhibited by the intervention of artist. Urine titled as "fountain" is still functional and have a place in the market. In another word, it is not rubbish.

%\todo{bir conslusion lazım buraya.}
